DataGatheringandAnalysis

### 2014-11-13 GEMDataSource.Rmd
Regressions Nascent Entrepreneurship, Established Owner

# Run a linear regression
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalGEM)
summary(R2)

@@

# Run a linear regression
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalGEM)
summary(R3)

>>>>

# Run a linear regression
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
           PercentOpportunities, data = CompleteDataset)
summary(R2)

@@

# Run a linear regression
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
           PercentOpportunities, data = CompleteDataset)
summary(R3)
